Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-27 Manuscript_draft.Rmd
update manuscript
Update Q2.1 forest plot

#added for now
asymptomaticQ2_1 <- asymptomaticQ2_1[asymptomaticQ2_1$record_id < "5296", ]

@@

#Note: Chaw is missing

@@

q2_1_asymp <- metabin(event.e = Ee,
                      n.e = Ne,
                      event.c = Ec,
                      n.c = Nc, 
                      data = q2_1_df,
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE, 
                      byvar = group)
q2_1_asymp

>>>>

#added for now
asymptomaticQ2_1 <- asymptomaticQ2_1[asymptomaticQ2_1$record_id < 5296, ]

@@

#cut data at end of jan 31
published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
q2_1_df <- q2_1_df %>%
  filter(record_id <= 5296 | record_id %in% published_preprints)

@@

q2_1_asymp <- metabin(event.e = Ee,
                      n.e = Ne,
                      event.c = Ec,
                      n.c = Nc, 
                      data = q2_1_df,
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE, 
                      byvar = group, 
                      comb.random = TRUE,
                      comb.fixed = FALSE)
q2_1_asymp
